Local PCA results

### 2016-05-25 medicago/summarize_run.Rmd
added abstract and discussion
.

@@

# set up to plot all chromosomes together
chrom.plot <- function (y,ylab='',main='',...) {
    plot(0, type='n', xlim=range(chrom.offsets/1e6), ylim=range(y,finite=TRUE), 
         xlab='', xaxt='n', ylab=ylab, main=main)
    for (k in 1:floor(length(chroms)/2)) {
        rect( xleft=chrom.dividers[2*k-1]/1e6, xright=chrom.dividers[2*k]/1e6, 
             ybottom=par("usr")[3], ytop=par("usr")[4], 
             border=NA, col=adjustcolor("grey",0.25) )
    }
    abline( v=chrom.dividers/1e6, lty=3, col=adjustcolor("grey",0.5), lwd=2 )
    axis( 1, at=chrom.mids/1e6, labels=chroms, las=0, tick=FALSE )
    points( regions$pos/1e6, y, ...)
}
```

>>>>

Render this, for instance, like:
```
templater::render_template("summarize_run.Rmd",output="lostruct/results_type_snp_size_10000_jobid_324902/run_summary.html",change.rootdir=TRUE)
```

@@

#' Set up to plot all chromosomes together
#' will plot the vector of values 'y' along all the chromosomes.
chrom.plot <- function (y,ylab='',main='',...) {
    plot(0, type='n', xlim=range(chrom.offsets/1e6), ylim=range(y,finite=TRUE), 
         xlab='', xaxt='n', ylab=ylab, main=main)
    for (k in 1:floor(length(chroms)/2)) {
        rect( xleft=chrom.dividers[2*k-1]/1e6, xright=chrom.dividers[2*k]/1e6, 
             ybottom=par("usr")[3], ytop=par("usr")[4], 
             border=NA, col=adjustcolor("grey",0.25) )
    }
    abline( v=chrom.dividers/1e6, lty=3, col=adjustcolor("grey",0.5), lwd=2 )
    axis( 1, at=chrom.mids/1e6, labels=chroms, las=0, tick=FALSE )
    points( regions$pos/1e6, y, ...)
}
```
